%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Evgenii Safronov} % Your name
\address{evgenii.safronov@iit.it} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
% \address{+393885816175}
% \address{Ph.D. student at Humanoid Sensing and Perception group, Italian Institute of Technology}
% \address{Genova, Italy}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Ph.D. student, Bioengineering and Robotics} \hfill {November 2019 - now}
\\ 
Universit\'a degli studi di Genova, Istituto Italiano di Tecnologia, Genova, Italy.
\\
{Supervisors: Dr. Lorenzo Natale and Dr. Michele Colledanchise -- Istituto Italiano di Tecnologia, Genova}


{\bf Master of Science, Space and Engineering Systems} \hfill {September 2017 - June 2019}
\\ 
Skolkovo Institute of Space and Technology (Skoltech), Moscow, Russia.
\\
GPA: 5.0/5
\\
{Thesis project: Development of Mission Execution System for Unmanned Aircraft Systems}
\\
{Supervisors: Dr. Ing. habil. Konstantin Kondak -- DLR, Germany,\\} 
{prof. Dzmitry Tsetserukou -- Skoltech, Russia}

{\bf Bachelor of Science, Applied Physics and Mathematics} \hfill {September 2013 - July 2017}
\\ 
Moscow Institute of Physics and Technology (MIPT), Dolgoprudnyy, Russia.
\\
GPA: 4.92/5
\\
Thesis project: Optimization of single and double superconducting qubit gates 
\\
Supervisors: Dr. Kirill Shulga, Gleb Fedorov -- Russian Quantum Center, Russia

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}


\begin{rSection}{Experience and Internships} \itemsep -3pt  
{Istituto Italiano di Tecnologia, Genova} \hfill November 2019 - now \\
{Sberbank Robotics Lab, internship, Moscow} \hfill July 2019 - October 2019 \\
{Master thesis internship, DLR/Elektra Solar GmbH, Munich} \hfill November 2018 - April 2019 \\ 
{Agrocompost LLC, Moscow} \hfill August 2018 - October 2018 \\
{Junior Researcher, Russian Quantum Center, Moscow} \hfill November 2016 - June 2017 \\
{Summer Internship, Helmholtz-Zentrum Berlin, Berlin} \hfill August 2016 - September 2016\\
{Website development, dati.mipt.ru} \hfill October 2015 - June 2016 \\
{Tutor in physics, math and programming, Moscow} \hfill September 2014 - May 2016 \\
\end{rSection} 


\begin{rSection}{Awards and Scholarships} \itemsep -3pt  
{Best Research Thesis - the best in the track, top 5\% of University, Skoltech} \hfill June 2019 \\
{Best Academic Excellence - top 10\% of University, Skoltech} \hfill June 2019 \\
{Eurobot 2019 Finals, Vice champions} \hfill June 2019 \\
{Skoltech's academic mobility grant} \hfill November 2018 - April 2019 \\  
{Eurobot 2018 Finals, 5th place} \hfill May 2018 \\
{Skoltech president stipend} \hfill November 2017 - June 2018 \\
{Letter from MIPT president in recognition of public achievements} \hfill November 2017\\
{International Olympiad in Theoretical Physics, Gold medal} \hfill 2017 \\
{Best general physics exam performance} \hfill June 2016 \\
{MIPT 'Abramovka' competitive stipend for excellent study} \hfill September 2014 - June 2016 \\
{All-Russian School Olympiad: regional winner for astronomy, physics, math and programming.} \hfill 2011 - 2013 \\
\end{rSection} 
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills and interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Research & Task planning under partial observability \\
Languages & C++, C, Python, JavaScript, CoffeeScript, Matlab, PHP\\ 
Other & Linux, ROS, OpenCV, SolidWorks\\  
Interests & table tennis, snowboarding, cinematography
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\pagebreak

\begin{rSection}{PROJECTS}

\begin{rSubsection}{Automated Planning under Uncertainties for Autonomous Robots}{November 2019 - now}{Ph.D. study at Uni. Genova \& Istituto Italiana di Tecnologia}
\item Task planning in partially observable, non deterministic environment
\end{rSubsection}

\begin{rSubsection}{Development of Mission Execution System for Unmanned Aircraft Systems}{November 2018 - May 2019}{Master Thesis Project}{} 
\item IEEE IROS 2019 conference contributed paper, 1st author
\item High altitude pseudo satellites project in collaboration with Elektra Solar GmbH
\item Control architecture 
\item Theoretical rework of behavior tree (BT) concept, novel variable-based approach for BT
\item State synchronization for 3 redundant flight control computers
\item C++ framework developed

\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{UAV relative to ground mobile robot localization}{2018, Summer}{Industrial Immersion Project in Warevision, Skoltech startup}{}
\item IEEE VTC 2019 Spring conference contributed paper, 2nd author
\item Localization system based on fusion of monocular camera and ultrasonic robot-to-UAV distance measurements.
\item UAV had 2 concentric IR active markers - smaller for landing and take-off, bigger for high altitude flights.
\item Choice of solution, Python/ROS framework development
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{Eurobot Open}{2018-2019}{Skoltech}{}
\item Champions of Russia, Vice champions of Europe
\item Leading mentor
\end{rSubsection}

\begin{rSubsection}{Eurobot Open}{2017-2018}{Skoltech}{}
\item Team Captain, Software Development
\item 1st place in Russia, 5th place in Europe (final stage).
\item 2 mobile collaborative robots from the scratch
\item Linux, Python/ROS, Odroid XU4, Behavior trees, IQP/Dynamic programming, LIDAR, Computer Vision
\item \href{https://github.com/SkoltechRobotics/ros-eurobot-2018}{ROS package} 
\item \href{https://youtu.be/9kTYelf_5CA?t=4115}{Performance sample on YouTube}
\end{rSubsection}

\begin{rSubsection}{Automated mission generation based on score rewards and tasks execution time
}{2017}{Skoltech, Optimization Methods Course}{}
\item Best project grade
\item \href{https://github.com/safoex/OptimizationMethods/blob/master/Project/Project\_s.ipynb}{Code \& presentation}
\end{rSubsection}

\begin{rSubsection}{"Magic wand"-like gesture recognition based on IMU sensor data }{2017}{Skoltech, Introduction to Data Science Course}{}
\item 96\% cross validated score (accuracy).  Best project grade
\item \href{https://github.com/MisterMap/MagicWand/blob/master/Gesture\%20classification\%20Presentation.ipynb}{Code \& presentation}
\end{rSubsection}

\begin{rSubsection}{Optimization of single and double superconducting qubit gates}{2016-2017}{MIPT, Russian Quantum Center, Bachelor Thesis Project}{}
\item Theoretical investigation and simulation of single and double qubit systems
\item \href{https://github.com/safoex/qubitlab}{Python framework development}
\end{rSubsection}



\end{rSection} 


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\iffalse

\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Mechanical Draftsman and Q.C Inspector}{May 2010 - May 2012} {Geeta Machine Tools Pvt. Ltd. Jamnagar} {} 
\item Prepare 2D AND 3D Drawing and planning of a different CNC machine details
parts drawings and their assembly drawing.
\item Do some quality control work for maintain the quality of machine in the Units.
\item Prepare of foundation and electrical layout drawings.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Lab Technician}{june 2012 - Auguest 2012}{Senor Metal Pvt. Ltd. Jamnagar} {}
 \item Do Some Mechanical Destructive Testing- Tensile Test, Impact Test,Hardness Test
\end{rSubsection}
 
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular Activities} \itemsep -1pt {}   
\item STTP on "Life Long Research" in SVNIT,Surat \hfill February 2016
\item Design War Cad, SRCOE, Rajkot, Secured 2rd rank in a state level competition\hfill January-2016
\item  Design War Cad, B.H Gardi, Rajkot, Secured 2rd rank in a
state level competition. \hfill January-2014 
\item Participated in National Level Technical Symposium Festival Edge and Above, SVIT, Vasad. \hfill February-2013
\item Participated in National Level Technical Symposium Festival Home Basix, SVIT, Vasad.
 \hfill  February-2013 
\item Participated in National Level Technical Symposium Rise of Machine, SVIT, Vasad,  \hfill March-2014 
 

\end{rSection}
\fi
\end{document}
